Interisland movements of woodland caribou in Newfoundland

### 2020-02-21 paper/manuscript.Rmd
Update manuscript.Rmd and ~$nuscript.docx

<!-- Caribou were introduced to Fogo Island (n = 26 animals between 1964–67) and
Change Island (n = 5 animals in 1964) from the main Island of Newfoundland as
part of a series of translocations and introductions throughout the province
(Bergerud & Mercer 1989). Since 2016 we have been studying the Fogo Island
caribou herd (Bonar et al. 2017; Bonar et al. 2018; Peignier et al. 2019). To
date, we have fitted 29 adult female caribou with GPS collars (1240g, GPS 4400M;
Lotek Wireless Inc., Newmarket, Ontario, Canada), which were programmed to
collect relocation fixes every 2 hours (see Bonar et al. 2018 for details). We
used GPS locations from these individuals to investigate oceanic swimming
events. -->

@@

Historic predators of caribou such as wolves (*Canis lupus*) and black bears
(*Ursus americanus*) are not present in the Fogo Island archipelago; coyotes
(*Canis latrans*) are the top predator in this region. Predation by coyotes on
adult caribou is relatively rare (ref?), so the potential effect of predators on
caribou swimming behaviour is likely to be a flight response to non-lethal
encounters. Calves are susceptible to coyotes, particularly young calves, but
the energetic costs to oceanic swimming for calves is likely to be far greater for small
calves compared to adults.

>>>>

<!-- Caribou were introduced to Fogo Island (n = 26 animals between 1964–67) and
Change Island (n = 5 animals in 1964) from the main Island of Newfoundland as
part of a series of translocations and introductions throughout the province
(Bergerud & Mercer 1989).

@@

Historic predators of caribou such as wolves (*Canis lupus*) and black bears
(*Ursus americanus*) are not present in the Fogo Island archipelago, thus
leaving coyotes (*Canis latrans*) as the top predator. Predation by coyotes on
adult caribou is relatively rare [@Bastille_Rousseau_2016], so the potential
effect of predators on caribou swimming behaviour is limited to non-consumptive
effects associated with encounters and subsequent flight response. Adult females
with calves at heel may be an exception because calves are highly susceptible to
coyotes [@Rayl_2014], but the energetic costs for calves to swim in the ocean is
likely far greater than adults. As one might expect, none <!--confirm--> of the
86 swimming events we observed occurred in the weeks after calves were born,
suggesting swimming with in the ocean with a calf-at-heel is likely more risky
than other predator avoidance behaviours.
